\chapter{Approach}
\label{chp:Approach}
To identify the right domain size and boundary conditions, I will conduct 2D spinning circle simulations at $\Omega^{\ast} = 1, 3$ with periodic and symmetric boundary conditions. The three different domain heights that will be tested are $40D, 80D, 120D$. The main purpose of the $\Omega^{\ast}=1$ cases is to find which boundary conditions and domain size satisfy our needs, since our parameter sweep will occur at $\Omega^{\ast}=1$. We will see at what domain size are the values of drag insensitive to changes in boundary conditions and domains height. The main purpose of the $\Omega^{\ast}=3$ cases is to identify the physics, since the effects will be obvious. We will plot the surface pressure distribution of the circles to see how the pressure distribution shifts. 

To validate the Schwarz-SEM (Neknek) framework for spinning ellipses, I will run simulations in homogeneous flow. I will compare the drag and lift values to those of \cite{lu_flow_2018} and \cite{lua_rotating_2018}. To validate the framework for static circles in stratified flows I will run monodomain and Schwarz-SEM cases of static circular cylinders in a stratified cross-flow. I will compare the drag and lift coefficients. I will conduct mesh independence tests by finding an edge case and running a simulation with increased polynolial order and decreased polynomial order to see it make a difference in drag and lift. 

To find the effect of stratification and spin on flow I will run a parameter sweep of spinning and nonspinning circular cylinders and spinning ellipses of varying aspect ratios. 
\input{3.1_governing_equations_and_setup}
\input{3.2_schwarz-SEM_framework}
\input{3.3_validation}