%
%  Time-stamp: "[abstract.tex] last modified by Scott Budge (scott) on 2017-01-10 (Tuesday, 10 January 2017) at 16:54:14 on goga.ece.usu.edu"
%
%  Info: $Id: abstract.tex 998 2017-03-21 16:44:33Z scott $   USU
%  Revision: $Rev: 998 $
% $LastChangedDate: 2017-03-21 10:44:33 -0600 (Tue, 21 Mar 2017) $
% $LastChangedBy: scott $
%

\begin{abstract}
% A space is needed before the text starts so that the first paragraph
% is indented properly.

Direct Numerical Simulations (DNS) are performed on rotating 2D bodies in incompressible stratified flow. The effects of rotation, shape, and stratification on drag, lift, and flow structures such as internal gravity waves (IGW) are investigated. The Schwarz-spectral element method (Schwarz-SEM) is utilized through the use of a static background mesh and a rotating, conforming mesh to account for rotation and noncircular shapes; the meshes overlap for data exchange. The Boussinesq approximation is utilized to account for the effects of stratification in the Navier-Stokes equations. This Schwarz-SEM framework in stratification is validated against literature and established methods. We conduct cycle-averaging and phase-averaging of the drag and lift on the ellipses to isolate the different ways in which drag and lift are affected by the parameters of interest. We conduct a Hilbert transformation of the fields of the results to investigate directionality of the IGW by extracting the wave numbers in each direction. We run static and rotating circular cylinder simulation cases, along rotating ellipse cases of two different noncircular aspect ratios. We run simulations at different stratification levels, along with simulations in homogeneous flows. 

\end{abstract}


% Local Variables:
% TeX-master: "newhead"
% End:
