%
%  This is an example of how a LaTeX thesis should be formatted.  This
%  document contains chapter 2 of the thesis.
%
%  Time-stamp: "[sample-chapter2.tex] last modified by Scott Budge (scott) on 2016-07-28 (Thursday, 28 July 2016) at 08:40:50 on goga.ece.usu.edu"
%
%  Info: $Id: sample-chapter2.tex 967 2016-07-28 15:33:29Z scott $   USU
%  Revision: $Rev: 967 $
% $LastChangedDate: 2016-07-28 09:33:29 -0600 (Thu, 28 Jul 2016) $
% $LastChangedBy: scott $
%

\chapter{Objectives}
\label{chp:Objectives}

\begin{enumerate}
	\item I will identify the physical effects that causes differences in drag, and use this knowledge to identify good lateral boundary conditions and domain height.
	\begin{enumerate}
		\item I will identify why drag results are different when the lateral boundary condition are symmetric versus periodic. 
		\item I will identify why drag results are different when the height of the domain changes. 
	\end{enumerate}
	\item I will validate Neknek and Schwarz-SEM framework for spinning ellipses in stratified flows.
	\begin{enumerate}
		\item I will validate framework for spinning ellipses in homogeneous flows with existing literature.
		\item I will validate this framework for static circles in stratified flows using a mono-domain simulation based on an well-know Nek5000 example.  		
		\item I will conduct a mesh independence test 
	\end{enumerate}
	\item I will find the effect of stratification on flow around spinning bodies.
	\begin{enumerate}
		\item I will compare drag and lift values for bodies across different $Fr^2$.
		\item I will compare schlerien and y-velocity field plots of flow around bodies for different $Fr^2$.
	\end{enumerate}
	\item I will find the effect of spin on flow around circular cylinders in stratified flow.
	\begin{enumerate}
		\item I will compare drag and lift values for cylinders of $\Omega^{\ast} = 0, 1$ 
		\item I will compare schlerien and y-velocity field plots of flow around cylinders of $\Omega^{\ast} = 0, 1$ 
	\end{enumerate}
\end{enumerate}
